Language-Based Security for Low-Level MPC

### 2024-05-20 ppdp24/example-gmw.tex
checkpoint
tweak to intro

To properly integrate the local reasoning of Lemma \ref{lemma-gmwtactic} with
the global reasoning of Lemma \ref{lemma-gmwinvariant}, we can demonstrate
the following.
\begin{lemma}
  \label{lemma-conditioning}
  Each of the following hold:
  \begin{enumerate}
    \item Given $\condp{\pmf}{X_1}{\detx{X_2}}$ and
      $\condp{\pmf}{X_2}{\detx{X_3}}$, then $\condp{\pmf}{X_1}{\detx{X_3}}$.
    \item Given $\condp{\pmf}{X_1}{\detx{X_2}}$ and
      $\condsep{\pmf}{X_2}{X_3}{X_4}$, then $\condsep{\pmf}{X_1}{X_3}{X_4}$.
    \item Given $\condsep{\pmf}{X_1}{X_2}{X_3}$ and $\condp{\pmf}{X_1}{\detx{X_2}}$
      and $\condp{\pmf}{X_2}{\detx{X_4}}$, then $\condsep{\pmf}{X_1}{X_4}{X_3}$.
    \item Given $\condsep{\pmf}{X_1 \cup X_2}{X_3}{X_4}$ and $\condp{\pmf}{X_1 \cup X_2}{\detx{X_2}}$,
      then $\condsep{\pmf}{X_1}{X_2 \cup X_3}{X_4}$.
  \end{enumerate}
\end{lemma}

@@

  \conddetx{\progtt(\prog)}{S^1}{\{ \macgv{\mesg{x}} \}}    
  \end{mathpar}
  This, together with Lemma \ref{lemma-gmwtactic} (1) and Lemma \ref{lemma-conditioning} (1)
  give:
  $$
  \conddetx{\progtt(\prog)}{S^1 \cup S^2}{\{ \macgv{\mesg{z}} \}}
  $$
  and Lemma  \ref{lemma-gmwtactic} (2) and Lemma \ref{lemma-conditioning} (2-3) gives:
  $$
  \begin{array}{c}
    \progtt(\prog)|S^1 \cup S^2) \vdash \\
    {\{ \macgv{\mesg{z}} \}}{(M^1_C \cup M^2_C \cup \{ \elab{\mesg{x}}{2}, \elab{\mesg{y}}{2}, \elab{\mesg{z}}{1}, \elab{\mesg{z}}{2} \})}
  \end{array}
  $$
\end{proof}

@@

    \condsep{\progtt(\prog)}{S}{\{\macgv{\mesg{z}}\}}{(M_C \cup \{ \elab{\mesg{z}}{1}, \elab{\mesg{z}}{2} \})}
  \end{mathpar}
  so also by definition of $\decodegmw$ we have:
  \begin{mathpar}
    \conddetx{\progtt(\prog)}{S_H \cup S_C}{O}

    \condsep{\progtt(\prog)}{S_H \cup S_C}{O}{(M_C \cup P)}
  \end{mathpar}
  and this by Lemma \ref{lemma-conditioning} (4) we have:
  $$
  \condsep{\progtt(\prog)}{S_C}{(O \cup S_H)}{(M_C \cup P)}
  $$
  which implies the result.
\end{proof}

>>>>

To properly integrate the local reasoning of Lemma \ref{lemma-gmwtactic} with
the global reasoning of Lemma \ref{lemma-gmwinvariant}, we can demonstrate
the following.
\begin{lemma}
  \label{lemma-conditioning}
  Each of the following hold:
  \begin{enumerate}
    \item Given $\condp{\pmf}{X_1}{\detx{X_2}}$ and
      $\condp{\pmf}{X_2}{\detx{X_3}}$, then $\condp{\pmf}{X_1}{\detx{X_3}}$.
    \item Given $\condp{\pmf}{X_1}{\detx{X_2}}$ and
      $\condsep{\pmf}{X_2}{X_3}{X_4}$, then $\condsep{\pmf}{X_1}{X_3}{X_4}$.
    \item Given $\condsep{\pmf}{X_1}{X_2}{X_3}$ and $\condp{\pmf}{X_1}{\detx{X_2}}$
      and $\condp{\pmf}{X_2}{\detx{X_4}}$, then $\condsep{\pmf}{X_1}{X_4}{X_3}$.
    \item Given $\condsep{\pmf}{X_1 \cup X_2}{X_3}{X_4}$ and $\condp{\pmf}{X_1 \cup X_2}{\detx{X_3}}$,
      then $\condsep{\pmf}{X_1}{X_2 \cup X_3}{X_4}$.
  \end{enumerate}
\end{lemma}

@@

  \conddetx{\progtt(\prog)}{S^2}{\{ \macgv{\mesg{y}} \}}    
  \end{mathpar}
  This, together with Lemma \ref{lemma-gmwtactic} (1) and Lemma \ref{lemma-conditioning} (1)
  give:
  $$
  \conddetx{\progtt(\prog)}{S^1 \cup S^2}{\{ \macgv{\mesg{z}} \}}
  $$
  and Lemma  \ref{lemma-gmwtactic} (2) and Lemma \ref{lemma-conditioning} (2-3) gives:
  $$
  \begin{array}{c}
    \progtt(\prog)|S^1 \cup S^2) \vdash \\
    {\{ \macgv{\mesg{z}} \}} * {(M^1_C \cup M^2_C \cup \{ \elab{\mesg{x}}{2}, \elab{\mesg{y}}{2}, \elab{\mesg{z}}{1}, \elab{\mesg{z}}{2} \})}
  \end{array}
  $$
\end{proof}

@@

    \condsep{\progtt(\prog)}{S}{\{\macgv{\mesg{z}}\}}{(M_C \cup \{ \elab{\mesg{z}}{1}, \elab{\mesg{z}}{2} \})}
  \end{mathpar}
  and by definition of $\decodegmw$ the value $\{\macgv{\mesg{z}}\}$ is output
  after the parties publicly reveal $\{ \elab{\mesg{z}}{1}, \elab{\mesg{z}}{2} \}$, so we have:
  \begin{mathpar}
    \conddetx{\progtt(\prog)}{S_H \cup S_C}{O}

    \condsep{\progtt(\prog)}{S_H \cup S_C}{O}{(M_C \cup P)}
  \end{mathpar}
  and thus by Lemma \ref{lemma-conditioning} (4) we have:
  $$
  \condsep{\progtt(\prog)}{S_C}{(O \cup S_H)}{(M_C \cup P)}
  $$
  which implies the result.
\end{proof}
